Real Time Genome Scan Using GPU

### 2019-07-03 paper.tex
adding in details in *acceleration techniques* part

\subsection{Acceleration Techniques}
We used various techniques to accelerate eQTL scans. 
\subsubsection{Multithreaded CPU operations}
\subsubsection{Matrix and Vectorized Operations}
\subsubsection{Single precision}
\subsubsection{GPU operations}
\subsubsection{Julia language}

>>>>

\subsection{Acceleration Techniques}
We used various techniques to accelerate eQTL scans. 
\subsubsection{Multithreaded CPU operations}
 Used for multi-threaded loops whenever possible, eg. for element-wise operations
\subsubsection{Matrix and Vectorized Operations}
 OpenBLAS for multi-threaded matrix operations. 
Matrix multiplication is a well studied area where the computer scientists try to apply various optimization techniques to make it run faster. 
There are various BLAS libraries available, such as gslBLAS, OpenBLAS, etc. 
The matrix multiplication in OpenBLAS is default multithreaded, therefore does not require extra coding effort to achieve highly efficient result.

\subsubsection{Single precision}
 Faster and memory efficient; may be less accurate, but acceptable for quick scan
Most dataset used in scientific computing are stored in double precision.

\subsubsection{GPU operations}
Specialized computations such as matrix multiplications and element-wise operations; requires additional programming effort
\subsubsection{Julia language}
Programming simplicity of interpreted languages with speed approaching compiled languages; GPU programming and linear algebra straightforward
\subsubsection{ Heritability grid}
For LMMs, considering a discrete grid of heritabilities enhances parallelization
